A Bayesian method for inference of fundamental stellar parameters

### 2013-10-17 paper/paper.tex
removed echelle_io and calibrate tools, included LkCa15

>>>>

\section{Processing TRES Data}
We flux calibrate TRES data, but because the reduction pipeline does not produce a ``sigma spectrum,'' we instead use the Poisson errors on each pixel. By taking the raw, still-blazed spectrum, in units of ``counts,'' we can find the Signal-to-Noise ratio by,
\begin{equation}
  S/N = \sqrt{ {\rm cts}}
\end{equation}
then the Noise-to-Signal ratio is the inverse of this
\begin{equation}
  N/S = \frac{1}{\sqrt{ {\rm cts}}}
\end{equation}
then the errors on the flux-calibrated spectrum (in ergs/s/A/cm2) is simply the flux spectrum multiplied by N/S.
